```{r warning=FALSE, include=FALSE, echo=FALSE, message=FALSE}
library(sparkline)
library(kableExtra)
source('overall_sketches.R')
source('spark_sketches.R')
```

```{r warning=FALSE, include=FALSE, echo=FALSE, message=FALSE}

stage_codes =  unlist(stage_list)
stage_list_codes = stages[stages$code %in% unlist(stage_list), 'stageId']


multi_overall_results = get_multi_overall(stage_list_codes) %>%
                            mutate(diffFirstS = diffFirstMs/1000,
                                   totalTimeS = totalTimeMs/1000)

multi_overall_wide_pos = multi_overall_results %>%
                            get_multi_stage_generic_wide(stage_list_codes,
                                                         'position')


multi_overall_wide_time = multi_overall_results %>%
                              get_multi_stage_generic_wide(stage_list_codes,
                                                           'totalTimeS')

multi_overall_wide_gap = multi_overall_results %>%
                            get_multi_stage_generic_wide(stage_list_codes,
                                                         'diffFirstS')
```

```{r warning=FALSE, include=FALSE, echo=FALSE, message=FALSE}
# TO DO - need to have a function that does WRC/class not overall top10
clean_top10 = function(df) {
  df %>% relabel_times_df(stage_list_codes, cars) %>%
          dplyr::arrange(!!as.symbol(stage_codes[length(stage_codes)])) %>%
          head(10)
}          

multi_stage_times = get_multi_stage_times(stage_list_codes)

multi_stage_times_wide = multi_stage_times %>%
                            get_multi_stage_times_wide(stage_list_codes) %>%
                            clean_top10()

multi_stage_wide_pos = multi_stage_times %>%
                              get_multi_stage_generic_wide(stage_list_codes,
                                                         'position')  %>%
                            clean_top10()
```

## Overall Position

Evolution of overall position:

```{r }
out_table = multi_overall_wide_pos %>%
                              map_stage_codes(stage_list_codes) %>%
                              map_driver_names(cars) %>% 
              dplyr::arrange(!!as.symbol(stage_codes[length(stage_codes)]))  %>% head(10)

#formattable(out_table,
#            align='c',
#                  list(area(col = stage_codes) ~ highlight_first()))
#kable(out_table)
kable(out_table, format = "html") %>%
  kable_styling() %>%
  kableExtra::scroll_box(width = "100%")
```

## Gap to Overall Leader at Each Stage End

The gap to stage leader, with table ordered by overall rally position at end of last recorded stage:

```{r}
multi_overall_wide_gap_top10 = multi_overall_wide_gap %>%
                              map_stage_codes(stage_list_codes) %>%
                              map_driver_names(cars) %>%
                      dplyr::arrange(!!as.symbol(stage_codes[length(stage_codes)])) %>%
                      head(10)

#kable(multi_overall_wide_gap_top10)
kable(multi_overall_wide_gap_top10, format = "html") %>%
  kable_styling() %>%
  kableExtra::scroll_box(width = "100%")
```

## Stage Position History

*Ranked according to position on last recorded stage __not__ overall position. The advantage of this ordering is that it helps register "surprise" arising from a perhaps unexpected stage winner. The chart gives the summary of stage rank evolution.*

```{r}
gt_stage_pos_plots = list()
multi_stage_long_pos = multi_stage_wide_pos %>%
                              pivot_longer(c(all_of(stage_codes)),
                                           names_to ="Stage",
                                           values_to ="Pos") %>%
                          mutate(Stage = factor(Stage,
                                                levels = stage_codes))

pos_range = 1:max(multi_stage_long_pos$Pos)

top10_codes = multi_stage_wide_pos$code
# Iterate through each driver in the top 10
for (c in 1:length(top10_codes)){
    # Add each plot to the plot list
    gt_stage_pos_plots[[length(gt_stage_pos_plots) + 1]] <-
        get_pos_chart(multi_stage_long_pos, top10_codes[c],
                      embed=T, aspect_ratio=3, size=5)
}

multi_stage_wide_pos$poschart = gt_stage_pos_plots

# TO DO - add Overall with coloured background?
formattable(multi_stage_wide_pos, align='c',
                  list(area(col = stage_codes) ~ highlight_first()))  %>%
as.htmlwidget()

```

## Stage Times

*Table order may be irregular...*

```{r}
#kable(multi_stage_times_wide)
kable(multi_stage_times_wide, format = "html") %>%
  kable_styling() %>%
  kableExtra::scroll_box(width = "100%")
```
