## Stage `r stage_code` Splits Analysis

Reports on splits

```{r results=FALSE, message=FALSE, warning=FALSE}
#library(formattable)

#stage_code = 'SS2'

splits = get_splits(eventId, stageId)
splits_locations = splits$splitPoints
splits_list = splits_locations$splitPointId
splits_locations$splitname = sapply(splits_locations$splitPointId,
                                 get_split_label)

split_names = splits_locations$splitname
split_cols = get_split_cols(splits)
split_names = c(split_names, 'split_N')
```


```{r echo=FALSE, message=FALSE, warning=FALSE,}
full_splits_wide = get_splits_wide(splits, wrc_entries) %>%
                      widen_splits_stage_times(stage_times) %>%
                      map_split_codes(splits_list) %>% 
                      map_driver_names(cars)  %>%
              # Filter out any driver with an excessive delta
              #https://dplyr.tidyverse.org/reference/filter_all.html
                      #filter_at(vars(starts_with("split_")),
                      #          all_vars(abs(.) <20))
                      filter(diffFirstMs<30000)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
full_durations_wide = get_split_duration(full_splits_wide,
                                          split_names, id_col='code')
```

### Stage Split Times and Overall Stage Result

Summary of stage split times and overall stage result:

```{r}
stage_split_results = full_splits_wide %>% 
                  mutate(diffFirstS=diffFirstMs/1000) %>% 
                  select(c(code,  all_of(split_names),
                         diffFirstS, position)) %>% 
                  arrange(position)

kable(stage_split_results)
```


### Split Time Rankings

Rank of each split time:

```{r echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
split_ranks = get_split_rank(full_splits_wide, split_names) %>%
                select(code, all_of(split_names))

split_N_col_idx = which(colnames(split_ranks) == 'split_N')[[1]]
formattable(split_ranks, align='c',
            list(area(col = 2:split_N_col_idx) ~ color_tile2(c("red",'white', "forestgreen")),
                 entryId=FALSE))
```

### Ultimate Stage Comparisons

Split time comparisons relative to various ultimage stage time calculations.

These views provide various ways of comparing the performance of each driver to various ghost drivers:

- best recorded split time at each split (*ultimate actuals*): gives an estimate of how well the driver's split times compare with each first ranked split time (time into stage at each split);
- fastest time going from one split to the next (*ultimate sections*): gives an estimate of how quickly each driver completed each split section relative to the quickest time recorded completing that split section (time taken to go from one split point to the next);
- *accumulated ultimate sections* times: gives and estimate of how quickly the driver is going relative to the fastest possible completion of the stage based on accumulated ultimate split section times.


```{r echo=FALSE, message=FALSE, warning=FALSE}
ultimate_splits_long = full_durations_wide %>%
                     pivot_longer(all_of(split_names),
                                  names_to = "splitname",
                                  values_to = "sectionDurationS") %>%
                     select(splitname, sectionDurationS) %>%
                     # Defensive measure
                     filter(!is.na(sectionDurationS) & sectionDurationS>0) %>%
                     group_by(splitname) %>% 
                     summarise(ultimate = min(sectionDurationS,
                                              na.rm = TRUE)) %>%
                     mutate(ultimateElapsed = cumsum(ultimate))

ultimate_wide_durations = ultimate_splits_long %>% 
                  select(splitname, ultimate) %>%
                  pivot_wider(names_from = splitname,
                              values_from = ultimate) %>%
                  mutate(code='ultimate')

ultimate_between_split = full_durations_wide %>%
                            select(code, all_of(split_names)) %>% 
                            bind_rows(ultimate_wide_durations) %>%
                            rebase('ultimate', split_names,
                                   id_col='code')

ultimate_wide_elapsed = ultimate_widen(ultimate_splits_long,
                                       'ultimateElapsed', 'ultimate')

ultimate_accumulated = full_splits_wide %>% 
                          ultimate_rebaser(ultimate_wide_elapsed,
                                         split_names, 'ultimate')

actual_ultimate = full_splits_wide %>% 
                      select(code, all_of(split_names)) %>% 
                      # Make long
                      select(all_of(as.character(split_names)),
                             code) %>%
                      pivot_longer(as.character(split_names),
                                   names_to = "splitname",
                                   values_to = "sectionDurationS") %>%
                      group_by(splitname) %>%
                      summarise(actualUltimate = min(sectionDurationS,
                                                     na.rm=TRUE))

ultimate_splits_long$actual = actual_ultimate$actualUltimate
ultimate_wide_actual = ultimate_widen(ultimate_splits_long,
                                      'actual',
                                      'ultimate')
ultimate_actual = full_splits_wide %>% 
                      ultimate_rebaser(ultimate_wide_actual,
                                       split_names, 'ultimate')

```

#### Ultimate Actuals

Driver times compared to the first ranked recorded split time at each split:

```{r}
formattable(ultimate_actual, align='c',
            list(area(col = 2:split_N_col_idx) ~ color_tile2(c("red",'white', "forestgreen")),
                 entryId=FALSE))
```


#### Ultimate Sections

Split durations rebased relative to the fastest transit of each split section:

```{r echo=FALSE, message=FALSE, warning=FALSE}
formattable(ultimate_between_split, align='c',
            list(area(col = 2:split_N_col_idx) ~ color_tile2(c("red",'white',"forestgreen")),
                 entryId=FALSE))
```


#### Ultimate Accumulated Sections

Actual split times relative to the accumulated ultimate split section times:

```{r}
formattable(ultimate_accumulated, align='c',
            list(area(col = 2:split_N_col_idx) ~ color_tile2(c("red",'white', "forestgreen")),
                 entryId=FALSE))
```


